%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{enumitem}
\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}

%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%% NAME OF APPLICANT %%%%%%%%%%%%%%%%%%%

\centering \noindent  \LARGE{\textbf{Emilio Molina Martínez}}  \\
%\vspace{-2ex}
\noindent\rule{16cm}{0.4pt}
%\vspace{2ex}
\normalsize

%%%%%%%%%%%%%%%%% CONTACT INFORMATION %%%%%%%%%%%%%%%%%
% Your email address, website, and Skype name are links to send email, open your website and add you on Skype. 

\begin{center}
\textbf{Phone}: +34 610373998\\
\textbf{Email}: emilio.mol.mar@gmail.com\\
\textbf{Date of birth}: 2/5/1985\\
\textbf{Nationality}: Spanish\\
\textbf{Website}: \url{www.emiliomm.com}\\
\end{center}

\vspace{1em}

%%%%%%%%%%%%%%%%% MAIN BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%
% The main body is contained in a tabular environment. To move sections onto the next page, simply end the tabular environment and begin a new tabular environment.
\small
\noindent \begin{tabularx}{\linewidth}{l X}
 \Large{\textbf{Experience}}    & \textbf{R\&D Engineer} \hfill January 2015 $\rightarrow$\\
     & BMAT Licensing S.L.\\
     & \vspace{-0.1cm}\begin{itemize}[nosep,noitemsep,topsep=0pt,partopsep=0pt]
         \item Development of production-ready technologies in C++ and Python
         \item Development of web-based research tools for QA (Django) 
         \item Research on robust audio fingerprinting in challenging environments
         \item Research on music detection in broadcast audio
         \item Supervision of industrial PhD on music detection using deep learning
         \item R\&D team management tasks: OKRs planning, scrum, recruiting...
     \end{itemize}\\
     & \\
     & \textbf{Assistant Professor} \hfill October 2020 - December 2020\\
     & Universitat Pompeu Fabra\\
     & \vspace{-0.1cm}\begin{itemize}[nosep,noitemsep,topsep=0pt,partopsep=0pt]
         \item Part-time assistant professor for subject "Audio and Video Encoding Systems"
         \item Responsible for laboratory classes and material
     \end{itemize}\\
     & \\
     & \textbf{Research Academic Staff} \hfill January 2012 - January 2015\\
     & ATIC Research Group, University of Málaga\\
     & \vspace{-0.1cm}\begin{itemize}[nosep,noitemsep,topsep=0pt,partopsep=0pt]
         \item Research on singing / speech analysis with music applications
         \item Published several papers that eventually led to my PhD Thesis
         \item Development of demos in Matlab and C++
     \end{itemize}\\
     \\
\end{tabularx}
\noindent \begin{tabularx}{\linewidth}{l X}
 \Large{\textbf{Education}}    & \textbf{PhD in Telecommunication Engineering} \hfill Thesis Defense: July 2017\\
     & ATIC Research Group, University of Málaga\\
     & \vspace{-0.1cm}\begin{itemize}[nosep,noitemsep,topsep=0pt,partopsep=0pt]
         \item Title: ``Singing Information Processing: Techniques and Applications''
         \item Supervisors: Ana María Barbancho and Lorenzo J. Tardón
     \end{itemize}
     \\
     &\\
     & \textbf{Sound and Music Computing Master} \hfill Sept. 2010 - June 2012\\
     & Music Technology Group, Universitat Pompeu Fabra\\
     & MSc Thesis:``Automatic scoring of singing voice based on melodic similarity measures'' (Supervisors: Emilia Gómez \& Isabel Barbancho)
     \\
     &\\
     &\\
     & \textbf{Telecommunication Engineering} \hfill Sept. 2007 - March 2012\\
     & University of Málaga\\
     & \vspace{-0.1cm}\begin{itemize}[nosep,noitemsep,topsep=0pt,partopsep=0pt]
         \item Dissertation
         \item[] ``Software tool for the correction of dissonances in polyphonic music'', awarded the Finalist Ericsson National Prize on Applications for Multimedia Environments in May 2013
         \item Erasmus studentship at Polytech Lille (France) (Sept. 2009 - June 2011).
     \end{itemize}\\
     \\
\end{tabularx}
\noindent \begin{tabularx}{\linewidth}{l X}
     \hspace{2.5cm} & \textbf{Technical Telecommunication Engineering} \hfill Sept. 2003 - October 2007\\
     & Universidad de Málaga\\
     & \vspace{-0.1cm}\begin{itemize}[nosep,noitemsep,topsep=0pt,partopsep=0pt]
         \item Dissertation
         \item[] ``Multitrack environment for audio recording in C\#'', awarded the Best Project in Technical Telecommunication Engineering at University of Málaga in April 2008
         \item Award for the Best Academic Record in Technical Telecommunication Engineering at University of Málaga in 2007
     \end{itemize}\\
     \\
     & \textbf{\normalsize{Music education}}\\
     \\
     \hspace{2.5cm} & \textbf{Professional Degree of Classic Piano} \hfill Sept. 2004 - June 2011\\
     & Conservatori Profesional del Liceu (Barcelona) (2010-2011)\\
     & Conservatorio Profesional de Música Manuel Carra (Málaga) (2004-2010)\\
     & Elementary Degree: Conservatorio de Olula del Río (Almería) (1993-1998)\\
     &\\
     \\
\end{tabularx}
\\
\noindent \begin{tabularx}{\linewidth}{l X}
 \Large{\textbf{Online\hspace{0.9cm}}}    & \textbf{Deep Learning Nanodegree Foundation} \hfill January 2018\\
\Large{\textbf{courses}} & Udacity (www.udacity.com)\\
     & Projects: \url{https://github.com/EliosMolina/deep_learning_nanodegree}
     &\\
     \\
\end{tabularx}
\\
\noindent \begin{tabularx}{\linewidth}{l X}
\Large{\textbf{Languages}}    & \textbf{English:} Certificate in Advanced English (CAE) (July 2013)\\
    & (University of Cambridge)\\
    & \textbf{French:} DELF B2 French Certificate (May 2010)\\
    & (Université de Lille)\\
    & \textbf{Spanish:} Mother tonge\\
    & \\
    \\
\end{tabularx}
\noindent \begin{tabularx}{\linewidth}{l X}
\Large{\textbf{Interests /}}    & Hobbies: playing music (piano, guitar), reading, watching series/films, hanging out with friends, learning new skills, sport from time to time.\\
\Large{\textbf{Other}}    & Organizer of Music Production Workshop at Universidad de Málaga (2014) (Blog: http://produccionmusicaluma.blogspot.com.es/)\\
    & Organizer of I Forum of Telecommunication Enterprises at Universidad de Málaga (2014) (Website: http://feti.ajilet.com/)
\end{tabularx}
\newpage
\noindent \begin{tabularx}{\linewidth}{l X}
\Large{\textbf{Publications}} & \begin{itemize*}
 \small
 \itemsep1.3em 
 \item E. Molina, I. Barbancho, E. Gómez, A. M. Barbancho and L. J. Tardón, ``Fundamental
Frequency Alignment Vs. Note-Based Melodic Similarity For Singing Voice Assessment'',
\textit{Proceedings of ICASSP} 2013.

 \item A. M. Barbancho, I. Barbancho, L. J. Tardón and E. Molina, ``A Database of Piano Chords: An Engineering View of Harmony'', Springer, 2013.
 
 \item C. Roig, I. Barbancho, E. Molina, L. J. Tardón and A. M. Barbancho, ``Rumbator: A
Flamenco Rumba Cover Version Generator Based On Audio Processing at Note-Level'',
\textit{Proceedings of DAFx} 2013.
 
 \item E. Molina, A. M. Barbancho, L. J. Tardón and I. Barbancho, ``Dissonance Reduction In Polyphonic
Audio Using Harmonic Reorganization'', \textit{IEEE Transactions on Acoustics, Speech
and Audio Processing}, vol. 22, no. 2, pp. 325-334, Feb. 2014.

  \item E. Molina, I. Barbancho, A. M. Barbancho and L. J. Tardón, ``Parametric Model of Spectral
Envelope to Synthesize Realistic Intensity Variations in Singing Voice'', \textit{Proceedings of
ICASSP} 2014.

  \item E. Molina, L. J. Tardón, I. Barbancho and A. M. Barbancho, ``The Importance of F0 Tracking
in Query-By-Singing-Humming'', \textit{Proceedings of ISMIR} 2014.

  \item E. Molina, A. M. Barbancho, L. J. Tardón and I. Barbancho, ``Evaluation framework for
automatic singing transcription'', \textit{Proceedings of ISMIR} 2014.

  \item E. Molina, L. J. Tardón, A. M. Barbancho and I. Barbancho, ``SiPTH : Singing Transcription
Based on Hysteresis Defined on the Pitch-Time Curve'', \textit{IEEE Transactions on Acoustics,
Speech and Audio Processing}, vol. 23, no. 2, pp. 252-263, Feb. 2015.

  \item J. L. Santacruz, L. J. Tardón, I. Barbancho and E. Molina, ``VOICE2TUBA: Transforming singing
voice into a musical instrument'', Multimedia Tools And Applications, pp. 1-21, 2016.

  \item B. Meléndez, E. Molina, E. Gómez, ``BAT: An open-source, web-based audio events annotation tool'' in \textit{Proceedings of the 3rd Web Audio Conference}, 2017.
  
  \item B. Meléndez, E. Molina, E. Gómez, ``Music detection in broadcast audio recordings: a non-binary approach with relative loudness annotations'' in \textit{Proceedings of ISMIR} 2018.
 
 \item E. Molina, P. Cano, A. Ciurana, J. Lyda. ``Estimating audibility of audio samples''. European patent application 16192913.8 - 1910. Nov. 2016. (Accepted)
 
 \item E. Molina, A. Ciurana, P. Cano. ``Identifying background audio in broadcast signals using multiple sources''. European patent application 17382440.0 - 1901. July 2017.
 \end{itemize*}
\end{tabularx}

\newpage
\noindent \begin{tabularx}{\linewidth}{l X}
\Large{\textbf{Publications}\vspace{4cm}} & \begin{itemize*}
 \small
 \itemsep1.3em 

 \item B. Meléndez, E. Molina, E. Gómez, ``Relative music loudness estimation using temporal convolutional networks and a CNN feature extraction front-end'' in \textit{Proceedings of DAFX}, 2020.

 \item F. Yesiler, E. Molina, J. Serrà, and E. Gómez., ``Investigating the efficacy of music version retrieval systems for setlist identification'' in \textit{Proceedings of ICASSP}, 2021.
 \end{itemize*}
\end{tabularx}

\end{document}